Notes on Control Plane Inference

### 2021-05-25 inference.tex
close proof holes

\begin{figure}[htp]
  \[\begin{array}{r >{\triangleq}cl}
  \multicolumn{3}{l}{\denote{c}^\sigma : \Pkt \to \mathcal{P}(\Pkt)_\error }\\
  \denote{x := e}^\sigma\pkt && \{\pkt\{x \mapsto \edenote{e}\pkt\}\} \\
  \denote{\havoc x}^\sigma\pkt && \{ \pkt\{x \mapsto v\} \mid v \in \Value \} \\
    \denote{\assume b}^\sigma\pkt &&
    \begin{cases}
      \{\pkt\} & \pkt \models b \\
      \{\} & \textit{otherwise} \\
    \end{cases}\\
    \denote{\assert b}^\sigma\pkt &&
    \begin{cases}
      \{\pkt\} & \pkt \models b \\
      \error & \textit{otherwise}
    \end{cases} \\
    %% \denote{\havoc \rho}^\sigma\,\mu\,\pkt &&
    %% \{(\mu\{\rho \mapsto r\}, \pkt) \mid r \in \Row\} \\
    \denote{c_1;c_2}^\sigma\pkt&&
    %% \bigcup_{\pkt' \in \denote{c_1}^\sigma\pkt}\denote{c_2}^\sigma\pkt' \\
    {\denote{c_2}^\sigma}^\dagger\left(\denote{c_1}^\sigma\pkt\right)\\
    \denote{c_1 \choice c_2}^\sigma\pkt &&
    \denote{c_1}^\sigma\pkt \cup \denote{c_2}^\sigma\pkt \\
    %% \denote{\{c\}}^\sigma\,\mu\,\pkt &&
    %% \{(\mu,\pkt') \mid (\mu',\pkt') \in \denote{c}^\sigma\,\mu\,\pkt \}\\
    \denote{t.\apply()}^\sigma\,\pkt &&
    \begin{cases}
      \denote{c[\vec d/\vec x]}^\sigma\pkt,
      & \text{exists}~r = \argmin_i\{\pkt \models b_i\} \\
      & \text{where}~\lambda \vec x.~c = r.\action, \vec d = r.\data \\
      & \text{where}~b_i = t.\matchrow(\sigma(t.\id)[i]) \\
      \{\pkt\}, & \textit{if no such } r \textit{ exists}
    \end{cases}
  \end{array}\]
  \caption{Semantics of Commands. The dagger operator $(\cdot^\dagger) : (\Pkt \to
    \mathcal{P}(\Pkt)_\error) \to \mathcal{P}(\Pkt)_\error \to
    \mathcal{P}(\Pkt)_\error$ lifts a function that accepts packets to one that
    accepts elements of to the pointed powerset.}
  \label{fig:com-sem}
\end{figure}

@@

\begin{figure}[htp]
  \[\begin{array}{r cl}
  \multicolumn{3}{l}{\state\sigma_c : (\Value \to \Row^*) \to \BExpr} \\
  \state\sigma_c &\triangleq
  & \displaystyle\bigwedge_{ t \in \tables(c) }
  \left(
  \begin{array}{>{\displaystyle}l}
  \gamma_t.\miss = 1 \Leftrightarrow \gamma_t.\hitAction > |\sigma(t.\id)| \\
  \wedge \bigvee_{r_i \in \sigma(t.\id)} \rho = r_i  \\
  \wedge \bigwedge_{r_i \in \sigma(t.\id)} \gamma_t.\hitAction = i \Leftrightarrow \rho_t = r_i \\
  \wedge \bigwedge_{r_i \in \sigma(t.\id)} \left(\gamma_t.\hitAction \geq i \Leftrightarrow \bigwedge_{j=0}^{i-1} \neg t.\matchrow(r_j)[\gamma_t.\keys/t.\keys]\right)\\
  \end{array}\right)
  \end{array}
  \]
  \caption{Symbolic State Encoding}
  \label{fig:table-instrument}
\end{figure}

\begin{definition}[Projections]
  For a set of variables $S \subseteq \Var$, and a packet $\pkt$, write
  $\pkt|_S$ to be projection of $\pkt$ onto $S$. \todo{I guess this means
    packets are partial functions?} Formally,
  \[\pkt|_S \triangleq \{x \mapsto \pkt(x) \mid x \in S\}.\]
  Two packets $\pkt$,
  $\pkt'$ are equivalent up to $S \subseteq \Var$, written $\pkt =_S \pkt'$, iff
  $\pkt|_S = \pkt'|_s$. A set of packets $P$ is a subset of $P'$ up to $S$,
  written $P \subseteq_S P'$ iff for every packet $\pkt \in P$, there exists
  $\pkt' \in P'$ such that $\pkt =_S \pkt'$. Two sets of packets $P$ and $P'$
  are $S$-equivalent, written $P =_S P'$ iff $P \subseteq_S P'$ and $P \subseteq_S P'$.
\end{definition}

\begin{lemma}[Projection]
  For $c \in \Cmd$, $\fvs(c) \subseteq V \subseteq \Var$ and $P \subseteq \Pkt$ such that $\forall
  \pkt_1,\pkt_2 \in P, \pkt_1 =_V \pkt_2$, $\denote{c} P =_V \denote{c} P|_V$.

\end{lemma}

@@

      Now, we can write
      \[\bigcup_{a=0}^{|t.\action| - 1}\denote{t.\action[a](\rho_t.\data)}^\dagger H_a
       = \denote{t.\action[r_i.\action](r_i.\data)}^\dagger H_a
       \]

       Which is $V$-equivalent to $\denote{t.\action[r_i.\action](r_i.\data)}\,\pkt$. \todo{PROVE THIS LEMMA}
       The result follows by the IH on $t.\action[r_i.\action](r_i.\data)$.

@@

        Our assumption gives us that $\bigwedge_{j=1}^n \neg t.\matchrow(r_j)$,
        which means that $\gamma_t.\hitAction > n$, and that $\gamma_t.\miss =
        1$. Conclude that $H_a = \emptyset$ and $M \neq \emptyset$. Since $P =_V
        \{\pkt\}$, and $M$ is a nonempty refinement of $P$\todo{PROVE THIS
          LEMMA?}, conclude that $M =_V \{\pkt\}$. The result follows.
    \end{enumerate}

>>>>

\begin{figure}[htp]
  \[\begin{array}{r >{\triangleq}cl}
  \multicolumn{3}{l}{\denote{c}^\sigma : \Pkt \to \mathcal{P}(\Pkt)_\error }\\
  \denote{x := e}^\sigma\pkt && \{\pkt\{x \mapsto \edenote{e}\pkt\}\} \\
  \denote{\havoc x}^\sigma\pkt && \{ \pkt\{x \mapsto v\} \mid v \in \Value \} \\
    \denote{\assume b}^\sigma\pkt &&
    \begin{cases}
      \{\pkt\} & \pkt \models b \\
      \{\} & \textit{otherwis
e} \\
    \end{cases}\\
    \denote{\assert b}^\sigma\pkt &&
    \begin{cases}
      \{\pkt\} & \pkt \models b \\
      \error & \textit{otherwise}
    \end{cases} \\
    %% \denote{\havoc \rho}^\sigma\,\mu\,\pkt &&
    %% \{(\mu\{\rho \mapsto r\}, \pkt) \mid r \in \Row\} \\
    \denote{c_1;c_2}^\sigma\pkt&&
    %% \bigcup_{\pkt' \in \denote{c_1}^\sigma\pkt}\denote{c_2}^\sigma\pkt' \\
    {\denote{c_2}^\sigma}^\dagger\left(\denote{c_1}^\sigma\pkt\right)\\
    \denote{c_1 \choice c_2}^\sigma\pkt &&
    \denote{c_1}^\sigma\pkt \cup \denote{c_2}^\sigma\pkt \\
    %% \denote{\{c\}}^\sigma\,\mu\,\pkt &&
    %% \{(\mu,\pkt') \mid (\mu',\pkt') \in \denote{c}^\sigma\,\mu\,\pkt \}\\
    \denote{t.\apply()}^\sigma\,\pkt &&
    \begin{cases}
      \denote{c[\vec d/\vec x]}^\sigma\pkt,
      & \text{exists}~r = \argmin_i\{\pkt \models b_i\} \\
      & \text{where}~\lambda \vec x.~c = r.\action, \vec d = r.\data \\
      & \text{where}~b_i = t.\matchrow(\sigma(t.\id)[i]) \\
      \{\pkt\}, & \textit{if no such } r \textit{ exists}
    \end{cases}
  \end{array}\]
  \caption{Semantics of Commands. The dagger operator $(\cdot^\dagger) : (\Pkt \to
    \mathcal{P}(\Pkt)_\error) \to \mathcal{P}(\Pkt)_\error \to
    \mathcal{P}(\Pkt)_\error$ lifts a function that accepts packets to one that
    accepts elements of to the pointed powerset.}
  \label{fig:com-sem}
\end{figure}

\subsection{Lemmas}

\begin{lemma}[Assume-Currying]
  \label{lem:assume-currying}
  For $b_1,b_2 \in \BExpr$, $\sigma : \Value \to \Row^*$,
  \[\forall \pkt. \denote{\assume {b_1\wedge b_2}}^\sigma \pkt = \denote{\assume {b_1};\assume {b_2}}^\sigma \pkt\]
\end{lemma}
\begin{proof}
  Let $b_1,b_2,\sigma, \pkt$ be arbitrary. Compute using the definitions of $\denote\cdot$ and $\models$.
  \[\begin{array}{ll}
  \denote{\assume {b_1 \wedge b_2}}^\sigma \pkt \\
  = \{\pkt \mid \pkt \models b_1 \wedge b_2\} \\
  = \{\pkt \mid \pkt \models b_1, \pkt \models b_2\} \\
  = {\denote{\assume{b_1}}^\sigma}^\dagger\{\pkt \mid \pkt \models b_1\} \\
  = \denote{\assume{b_1}; \assume{b_2}}^\sigma \pkt
  \end{array}\]
\end{proof}

\begin{lemma}[Products and Sums]
  \label{lem:prod-sum}
  For $c_1,c_2, c_3 \in \Cmd$, $\sigma : \Value \to \Row^*$, $\pkt \in \Pkt$.
  $\denote{c_1;(c_2 \choice c_3)}^\sigma\pkt = \denote{c_1;c_2 \choice
    c_1;c_3}^\sigma\pkt$.
\end{lemma}
\begin{proof}
  Let $c_1,c_2,c_3$, $\sigma$, and $\pkt$ be given as above. Compute:
  \[
  \begin{array}{ll}
  \denote{c_1;(c_2 \choice c_3)}^\sigma \pkt \\
  = {\denote{c_2 \choice c_3}^\sigma}^\dagger\left(\denote{c_1}^\sigma\pkt\right) \\
  = {\denote{c_2}^\sigma}^\dagger\left(\denote{c_1}^\sigma \pkt\right)
  \cup {\denote{c_3}^\sigma}^\dagger\left(\denote{c_1}^\sigma \pkt\right) \\
  = {\denote{c_1;c_2}^\sigma}\pkt\cup {\denote{c_1;c_3}^\sigma}\pkt
  \end{array}
  \]
\end{proof}

\begin{lemma}[Disjoint Commutativity]
  \label{lem:disj-comm}
  For $c_1,c_2 \in \Cmd$, and $\sigma : \Value \to \Row^*$ if $\fvs(c_1) \cap
  \fvs(c_2) = \emptyset$, $ \forall \pkt \in \Pkt. \denote{c_1;c_2}^\sigma\pkt =
  \denote{c_2;c_1}^\sigma \pkt$.
\end{lemma}
\begin{proof}
  %% Let $c_1,c_2$, $\sigma$, and $\pkt$ be given as above. Assume $\fvs(c_1) \cap
  %% \fvs(c_2) = \emptyset$. Compute:
  %% \[
  %% \begin{array}{ll}
  %%   \denote{c_1;c_2}^\sigma \pkt =

  %% \end{array}
  %% \]
  \todo[inline]{prove}
\end{proof}

@@

\begin{figure}[htp]
  \[\begin{array}{r cl}
  \multicolumn{3}{l}{\state\sigma^t \in \BExpr} \\
  \state\sigma^t & \triangleq &
  \left(\begin{array}{>{\displaystyle}l}
  \gamma_t.\miss = 1 \Leftrightarrow \gamma_t.\hitAction > |\sigma(t.\id)| \\
  \wedge \bigvee_{r_i \in \sigma(t.\id)} \rho = r_i  \\
  \wedge \bigwedge_{r_i \in \sigma(t.\id)} \gamma_t.\hitAction = i \Leftrightarrow \rho_t = r_i \\
  \wedge \bigwedge_{r_i \in \sigma(t.\id)} \left(\gamma_t.\hitAction \geq i \Leftrightarrow \bigwedge_{j=0}^{i-1} \neg t.\matchrow(r_j)[\gamma_t.\keys/t.\keys]\right)\\
  \end{array}\right)\\\\

  \multicolumn{3}{l}{\state\sigma_c \in \BExpr} \\
  \state\sigma_c &\triangleq
  & \displaystyle\bigwedge_{ t \in \tables(c) } \state\sigma^t
  \end{array}
  \]
  \caption{Symbolic State Encoding}
  \label{fig:table-instrument}
\end{figure}

\begin{lemma}[Symbolic State distributes over Sequence]
  \label{lem:sigma-distrib-seq}
  For $\sigma : \Value \to \Row^*$, $c_1,c_2 \in \Cmd$,
  $\state\sigma_{c_1;c_2} \Leftrightarrow \state{\sigma}_{c_1}\wedge\state{\sigma}_{c_2}$
\end{lemma}

\begin{proof}
  Let $\sigma : \Value \to \Row^*$ and $c_1,c_2\in \Cmd$ be given. Notice that
  $\tables(c_1;c_2) = \tables(c_1) \cup \tables(c_2)$. Compute:
  \[
  \begin{array}{l >{\displaystyle}ll}
    \state\sigma_{c_1;c_2}
    & = \bigwedge_{ t \in \tables(c_1;c_2) } \state\sigma^t \\
    & = \bigwedge_{ t \in \tables(c_1)\cup \tables(c_2) } \state\sigma^t \\
    & = \bigwedge_{t \in \tables(c_1)} \state\sigma^t \wedge \bigwedge_{t \in \tables(c_2)} \state\sigma^t \\
    & = \state\sigma_{c_1} \wedge \state\sigma_{c_2}
  \end{array}
  \]
\end{proof}

\begin{lemma}[Symbolic State distributes over Choice]
  \label{lem:sigma-distrib-choice}
  For $\sigma : \Value \to \Row^*$, $c_1,c_2 \in \Cmd$,
  $\state\sigma_{c_1 \choice c_2} \Leftrightarrow \state{\sigma}_{c_1}\wedge\state{\sigma}_{c_2}$
\end{lemma}

\begin{proof}
  Let $\sigma : \Value \to \Row^*$ and $c_1,c_2\in \Cmd$ be given. Notice that
  $\tables(c_1 \choice c_2) = \tables(c_1) \cup \tables(c_2)$. Compute:
  \[
  \begin{array}{l >{\displaystyle}ll}
    \state\sigma_{c_1 \choice c_2}
    & = \bigwedge_{ t \in \tables(c_1 \choice c_2) } \state\sigma^t \\
    & = \bigwedge_{ t \in \tables(c_1)\cup \tables(c_2) } \state\sigma^t \\
    & = \bigwedge_{t \in \tables(c_1)} \state\sigma^t \wedge \bigwedge_{t \in \tables(c_2)} \state\sigma^t \\
    & = \state\sigma_{c_1} \wedge \state\sigma_{c_2}
  \end{array}
  \]
\end{proof}

\begin{definition}[Projections]
  For a set of variables $S \subseteq \Var$, and a packet $\pkt$, write
  $\pkt|_S$ to be projection of $\pkt$ onto $S$. \todo{I guess this means
    packets are partial functions?} Formally,
  \[\pkt|_S \triangleq \{x \mapsto \pkt(x) \mid x \in S\}.\]
  Two packets $\pkt$, $\pkt'$ are equivalent up to $S \subseteq \Var$, written
  $\pkt =_S \pkt'$, iff $\pkt|_S = \pkt'|_s$. A set of packets $P$ is a subset
  of $P'$ up to $S$, written $P \subseteq_S P'$ iff for every packet $\pkt \in
  P$, there exists $\pkt' \in P'$ such that $\pkt =_S \pkt'$. Two sets of
  packets $P$ and $P'$ are $S$-equivalent, written $P =_S P'$ iff $P \subseteq_S
  P'$ and $P \subseteq_S P'$. A set $P \subseteq \Pkt$ is a $V$-equivalence
  class if $\forall \pkt_1, \pkt_2 \in P$, $\pkt_1 =_V \pkt_2$.
\end{definition}

\begin{lemma}[Projection Union-Distributivity]
  \label{lem:proj-union-set}
  For all $P,Q \subseteq \Pkt$, $V \subseteq \Var$,
  $(P\cup Q)|_V = P|_V \cup Q|_V$
\end{lemma}

\begin{proof}
  Let $P,Q \subseteq \Pkt$ and $V \subseteq \Var$ be given. Compute:

  \[\begin{array}{ll}
  (P\cup Q)|_V\\
  = \{\pkt|_V \mid \pkt \in P\cup Q\}\\
  = \{\pkt|_V \mid \pkt \in P\}\cup \{\pkt|_V \mid \pkt \in Q\}\\
  = P|_V \cup Q|_V
  \end{array}\]
\end{proof}

\begin{lemma}[Projection Idempotence]
  \label{lem:proj-idem}
  For all $\pkt \in \Pkt$, $V \subseteq \Var$,
  $(\pkt|_V)|_V = \pkt|_V$
\end{lemma}

\begin{proof}
  Let $\pkt \in \Pkt$ and $V \subseteq \Var$ be given.
  \[\begin{array}{ll}
    (\pkt|_V)|_V \\
    = \{x \mapsto (\pkt|_V)(x) \mid x \in V\} & \text{by definition}\\
    = \{x \mapsto (\{y \mapsto \pkt(y) \mid y \in V\})(x) \mid x \in V\} & \text{by definition}\\
    = \{x \mapsto \pkt(x) \mid x \in V\} & \beta\text{-reduction}\\
    = \pkt|_V & \text{by definition}
  \end{array}\]
\end{proof}

\begin{lemma}[Projection Idempotence for Sets]
  \label{lem:proj-idem-set}
  For all $P \subseteq \Pkt$, $V \subseteq \Var$,
  $(P|_V)|_V = P|_V$
\end{lemma}

\begin{proof}
  Let $P \subseteq \Pkt$ and $V \subseteq \Var$ be given. Compute:
  \[\begin{array}{ll}
  (P|_V)|_V \\
  = \{\pkt|_V \mid \pkt \in P|_V\}
  & \text{by definition of } (\cdot)|_V : \mathcal{P}(\Pkt) \to \mathcal{P}(\Pkt) \\
  = \{\pkt|_V \mid \pkt \in \{\pkt'|_V \mid \pkt'\in P\}\}
  & \text{by definition of } (\cdot)|_V : \mathcal{P}(\Pkt) \to \mathcal{P}(\Pkt) \\
  = \{(\pkt|_V)|_V \mid \pkt \in P \}
  & \text{by set theory} \\
  = \{\pkt|_V \mid \pkt \in P\} & \text{by Lemma~\ref{lem:proj-idem}} \\
  = P|_V & \text{by definition of } (\cdot)|_V : \mathcal{P}(\Pkt) \to \mathcal{P}(\Pkt)
  \end{array}\]
\end{proof}

\begin{lemma}{Subset Implies Projected Subset}
  \label{lem:subset-proj}
  For $P,Q \subseteq \Pkt$, and $ V \subseteq \Var$,
  If $P \subseteq Q$ then $P \subseteq_V Q$.
\end{lemma}

\begin{proof}
Let $P,Q \subseteq \Pkt$ and $V \subseteq \Var$ be given. Assume $P \subseteq Q$,
to show that $P \subseteq_V Q$.

Let $\pkt \in P$. Since $P \subseteq Q$, $\pkt \in Q$. Notice that $\pkt =_V
\pkt$, so $P \subseteq_V Q$.
\end{proof}

\begin{lemma}{Equality Implies Projected Equality}
  \label{lem:equal-proj}
  For $P,Q \subseteq \Pkt$, and $ V \subseteq \Var$,
  If $P = Q$ then $P =_V Q$.
\end{lemma}

\begin{proof}
  By Lemma~\ref{lem:subset-proj}
\end{proof}

\begin{lemma}[Expression Projection]
  \label{lem:proj-expr}
  For every set of variables $V \subseteq \Var$, packet $\pkt \in \Pkt$ and
  expression $e \in \BVExpr$, such that $\efvs(e) \subseteq V$, $\edenote{e}\pkt =
  \edenote{e}(\pkt|_V)$.
\end{lemma}

\begin{proof}
  Let $V \subseteq \Var$ be given.
  Proceed by induction on $e$, leaving $\pkt$ arbitrary.
  \begin{enumerate}[align=left]
  \item[($e = v$)] Let $\pkt$ be given. $\edenote{v}\pkt = v = \edenote{v}{\pkt|_V}$
  \item[($e = x$)] Let $\pkt$ be given. Note that $\efvs(x) = \{x\} \subseteq V$. Compute:
    \[\begin{array}{ll}
    \edenote{x}(\pkt|_V) \\
    = (\pkt|_V)(x)
    & \text{by definition of }\edenote\cdot\\
    = \{y \mapsto \pkt(y) \mid y \in V\}(x)
    & \text{by definition of }(\cdot)|_V : \Pkt \to \Pkt\\
    = \pkt(x) & \text{since } x \in V
    \end{array}
    \]
  \item[($e = e_1 \binop e_2$)] Let $\pkt$ be given. Compute:
    \[\begin{array}{ll}
    \edenote{e_1 \binop e_2}\pkt \\
    = \edenote{e_1}\pkt \binop \edenote{e_2}\pkt & \text{definition of }\edenote\cdot \\
    = \edenote{e_1}(\pkt|_V) \binop \edenote{e_2}(\pkt|_V) & \text{by IHS since }\efvs(e_i) \subseteq \efvs(e_1 \binop e_2) \subseteq V, i = 1,2 \\
    = \edenote{e_1 \binop e_2}(\pkt|_V) & \text{definition of }\edenote\cdot
    \end{array}\]
  \item[($e = \unop e$)] Let $\pkt$ be given. Compute:
    \[\begin{array}{ll}
    \edenote{\unop e}\pkt \\
    = \unop \edenote{e}\pkt & \text{definition of }\edenote\cdot \\
    = \unop \edenote{e}(\pkt|_V) & \text{by IH, since } \efvs(e) = \efvs(\unop e) \subseteq V \\
    = \edenote{\unop e}(\pkt|_V) & \text{definition of }\edenote\cdot
    \end{array}\]
  \end{enumerate}
\end{proof}

\begin{lemma}[Satisfaction Projection]
  \label{lem:proj-satis}
  For every set of variables $V \subseteq \Var$, packet $\pkt \in \Pkt$ and
  boolean expression $b \in \BExpr$, such that $\bfvs(b) \subseteq V$,
  $\pkt \models b$ iff $\pkt|_V \models b$.
\end{lemma}

\begin{proof}
  Let $V \subseteq \Var$ be given.
  Proceed by induction on $b$, leaving $\pkt$ arbitrary.
  \begin{enumerate}[align=left]
  \item[($b = \FALSE$)] Immediate.
  \item[($b = b_1 \Rightarrow b_2$)]
    Let $\pkt$ be given. Compute:
    \[\begin{array}{ll}
    \pkt \models b_1 \Rightarrow b_2 \\
    \iff \pkt \not\models b_1 \text{or} \pkt\models b_2 & \text{by definition of } \models   \\
    \iff \pkt|_V \not\models b_1 \text{or} \pkt|_V \models b_2  & \text{by IHs, since} \bfvs(b_i) \subseteq \bfvs(b_1 \Rightarrow b_2) \subseteq V, i = 1,2  \\
    \iff \pkt|_V \models b_1 \Rightarrow b_2
    & \text{by definition of } \models
    \end{array}\]

  \item[($b = e_1 = e_2$)] Let $\pkt$ be given. Compute:
    \[\begin{array}{ll}
    \pkt \models e_1 = e_2 \\
    \iff \edenote{e_1}\pkt = \edenote{e_2}\pkt
    & \text{by definition of }\models \\
    \iff \edenote{e_1}(\pkt|_V) = \edenote{e_2}(\pkt|_V)
    & \text{by Lemma~\ref{lem:proj-expr}, since } \efvs(e_i) \subseteq \bfvs(e_1 = e_2) \subseteq V, i = 1,2 \\
    \iff \pkt|_V \models e_1 = e_2
    & \text{by definition of }\models
    \end{array}\]

  \end{enumerate}

\begin{lemma}[Projection-Denotation Commutativity]
  \label{lem:proj-den-comm}
  For a closed action $c \in \Cmd$, $\fvs(c) \subseteq V \subseteq \Var$ and
  $\pkt \in \Pkt$, $\denote{c} \pkt =_V \denote{c} \pkt|_V$.
\end{lemma}

\begin{proof}
  Proceed by induction on $c$, leaving $\pkt$ general.
  \begin{enumerate}[align=left]
  \item[$(c = x:=e)$] Let $\pkt$ be given. Compute:
    \[\begin{array}{ll}
    (\denote{x:=e} (\pkt|_V))|_V\\
    = ((\pkt|_V)\{x:=\edenote{e}(\pkt|_V)\})|_V
    & \text{definition} \\
    = ((\pkt|_V)\{x := \edenote{e}\pkt\})|_V
    & \text{By Lemma~\ref{lem:proj-expr} since } \fvs(e) \subseteq \fvs(x := e) \subseteq V \\
    = (\pkt\{x := \edenote{e}\pkt\}|_V)|_V
    & \text{since } x \in \fvs(x:=e) \subseteq V \\
    = ((\denote{x:=e}\pkt)|_V)|_V
    & \text{by definition of }\denote{\cdot}\\
    = (\denote{x:=e}\pkt)|_V
    & \text{by Lemma~\ref{lem:proj-idem}}
    \end{array}\]
    The result follows by definition of $=_V$.

  \item[$(c = \havoc x)$] Contradictory; $\havoc x$ is not an action.
  \item[$(c = \assume b)$]
    Let $\pkt$ be given. Compute:
    \[\begin{array}{ll}
    (\denote{\assume b} \pkt)|_V \\
    = (\{\pkt \mid \pkt \models b\})|_V
    & \text{definition of}\denote\cdot\\
    = ((\{\pkt \mid \pkt \models b\})|_V)|_V
    & \text{By Lemma~\ref{lem:proj-idem-set}} \\
    = (\{\pkt|_V \mid \pkt \models b\})|_V
    & \text{definition of }(\cdot)|_V : \mathcal P (\Pkt) \to \mathcal P (\Pkt) \\
    = (\{\pkt|_V \mid \pkt|_V \models b\})|_V
    & \text{By Lemma~\ref{lem:proj-satis} since } \fvs(b) \subseteq \fvs(\assume b) \subseteq V \\
    = (\denote{\assume b}(\pkt|_V))|_V
    & \text{by definition of}\denote\cdot
    \end{array}
    \]
    The result follows by definition of $=_V$.

  \item[$(c = \assert b)$] \textit{sim.}
  \item[$(c = c_1;c_2)$] Let $\pkt$ be given. Compute:
    \[\begin{array}{>{\displaystyle}ll}
    (\denote{c_1;c_2}\pkt)|_V \\
    = (\denote{c_2}^\dagger(\denote{c_1}\pkt))|_V
    & \text{definition of }\denote\cdot \\
    = \left(\bigcup_{\pkt' \in \denote{c_1} \pkt} \denote{c_2}\pkt'\right)|_V
    & \text{definition of }(\cdot)^\dagger \\
    = \bigcup_{\pkt' \in \denote{c_1} \pkt} (\denote{c_2}\pkt')|_V
    & \text{by Lemma~\ref{lem:proj-union-set}} \\
    = \bigcup_{\pkt' \in \denote{c_1}\pkt} (\denote{c_2}(\pkt'|_V))|_V
    & \text{IH}(c_2)  \\
    =\bigcup_{\pkt' \in (\denote{c_1}\pkt)|_V} (\denote{c_2} \pkt')|_V
    & \text{by set theory} \\
    = \bigcup_{\pkt' \in (\denote{c_1}(\pkt|_V))|_V} (\denote{c_2} \pkt')|_V
    & \text{by IH}(c_1) \\
    = \bigcup_{\pkt' \in \denote{c_1}(\pkt|_V)} (\denote{c_2} (\pkt'|_V))|_V
    & \text{by set theory} \\
    = \bigcup_{\pkt' \in \denote{c_1}(\pkt|_V)} ((\denote{c_2} \pkt')|_V)|_V
    & \text{by IH}(c_2) \\
    = \bigcup_{\pkt' \in \denote{c_1}(\pkt|_V)} (\denote{c_2} \pkt')|_V
    & \text{by Lemma~\ref{lem:proj-idem-set}} \\
    = \left(\bigcup_{\pkt' \in \denote{c_1}(\pkt|_V)} \denote{c_2}\pkt'\right)|_V
    & \text{by Lemma~\ref{lem:proj-union-set}} \\
    = \denote{c_2}^\dagger(\denote{c_1}(\pkt|_V))|_V
    & \text{By definition of }(\cdot)^\dagger\\
    = (\denote{c_1;c_2}(\pkt|_V))|_V
    & \text{By definition of }\denote\cdot
    \end{array}\]
    The result follows by definition of $=_V$.

  \item[$(c = c_1 \choice c_2)$] Let $\pkt$ be given.
    \[\begin{array}{ll}
    (\denote{c_1\choice c_2}\pkt)|_V \\
    = (\denote{c_1}\pkt \cup \denote{c_2}\pkt)|_V
    & \text{By definition of }\denote\cdot \\
    = (\denote{c_1}\pkt)|_V \cup (\denote{c_2}\pkt)|_V
    & \text{By Lemma~\ref{lem:proj-union-set}} \\
    = (\denote{c_1}(\pkt|_V))|_V \cup (\denote{c_2}(\pkt|_V))|_V
    & \text{By IHs} \\
    = ((\denote{c_1}(\pkt|_V) \cup \denote{c_2}(\pkt|_V))|_V)|_V
    & \text{By Lemma~\ref{lem:proj-union-set}} \\
    = (\denote{c_1}(\pkt|_V) \cup \denote{c_2}(\pkt|_V))|_V
    & \text{By Lemma~\ref{lem:proj-idem-set}}\\
    = (\denote{c_1 \choice c_2}(\pkt|_V))|_V
    & \text{By definition of }\denote\cdot \\
    \end{array}\]

    The result follows by definition of $=_V$.

  \item[$(c = t.\apply())$] Contradictory; $t.\apply()$ is not an action.
  \end{enumerate}

@@

      Now, we can write
      \[\bigcup_{a=0}^{|t.\action| - 1}\denote{t.\action[a](\rho_t.\data)}^\dagger H_a
       = \denote{t.\action[r_i.\action](r_i.\data)}^\dagger H_{r_i.\action}
       \]

       which is $V$-equivalent to
       $\denote{t.\action[r_i.\action](r_i.\data)}\,\pkt$ by
       Lemma~\ref{lem:proj-den-comm}. The result follows by the IH on
       $t.\action[r_i.\action](r_i.\data)$ and Lemma~\ref{lem:equal-proj}.

@@

        Our assumption gives us that $\bigwedge_{j=1}^n \neg t.\matchrow(r_j)$,
        which means that $\gamma_t.\hitAction > n$, and that $\gamma_t.\miss =
        1$. Conclude that $H_a = \emptyset$ and $M \neq \emptyset$. Since
        $\emptyset \neq M \subseteq P =_V \{\pkt\}$, $M =_V \{\pkt\}$ by
        Lemma~\ref{lem:subset-proj}. The result follows by
        Lemma~\ref{lem:equal-proj}.
    \end{enumerate}
